\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-19 paper.qmd
Updated Figure 10

@@

cell_count_scurve <- ggplot(df_bin_centroids_all, 
                            aes(x = reorder(as.factor(hexID), 
                                            -bin_counts), 
                                y = bin_counts,
                                group = as.factor(b1),
                                color = as.factor(b1))) + 
  geom_line() + 
  # geom_hline(yintercept = benchmark1, color = "black", linewidth=0.5, alpha = 0.5) +
  scale_colour_discrete_qualitative(palette = "Dark 3") +
  xlab("hexagon id (re-ordered)") + 
  ylab("bin count") +
  ggtitle("(a)") +
  theme(aspect.ratio = 0.75,
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, angle = 90),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 12),
        legend.text = element_text(size = 10),
        legend.key.size = unit(1, 'cm'),
        legend.key.height = unit(1, 'cm'))
```

@@

<!--To generate errors for different total number of bins-->
```{r}
#| label: bins-scurve
## To initialize benchmark values to remove low density hexagons
benchmark_rm_hex_vec <- append(seq(0, 0.99, by=0.1), c(benchmark1, 0.99))

@@

>>>>

centroids_df_scurve |>
  filter(bin1 == 7) |>
  ggplot(aes(x = as.factor(hexID), 
           y = std_counts,
           group = as.factor(buff),
           color = as.factor(buff))) + 
  geom_line() +
  scale_color_brewer(type = "qual")
```

@@

# cell_count_scurve <- ggplot(df_bin_centroids_all, 
#                             aes(x = reorder(as.factor(hexID), 
#                                             -bin_counts), 
#                                 y = bin_counts,
#                                 group = as.factor(b1),
#                                 color = as.factor(b1))) + 
#   geom_line() + 
#   # geom_hline(yintercept = benchmark1, color = "black", linewidth=0.5, alpha = 0.5) +
#   scale_colour_discrete_qualitative(palette = "Dark 3") +
#   xlab("hexagon id (re-ordered)") + 
#   ylab("bin count") +
#   ggtitle("(a)") +
#   theme(aspect.ratio = 0.75,
#         axis.title.x = element_text(size = 12),
#         axis.title.y = element_text(size = 12, angle = 90),
#         axis.text.x = element_blank(),
#         axis.text.y = element_text(size = 12),
#         plot.title = element_text(size = 12),
#         legend.text = element_text(size = 10),
#         legend.key.size = unit(1, 'cm'),
#         legend.key.height = unit(1, 'cm'))

cell_count_scurve <- ggplot(df_bin_centroids_all, 
                            aes(x = as.factor(hexID), 
                                y = std_counts,
                                group = as.factor(b1),
                                color = as.factor(b1))) + 
  geom_line() + 
  # geom_hline(yintercept = benchmark1, color = "black", linewidth=0.5, alpha = 0.5) +
  scale_colour_discrete_qualitative(palette = "Dark 3") +
  xlab("hexagon id (re-ordered)") + 
  ylab("standardised bin count") +
  ggtitle("(a)") +
  theme(aspect.ratio = 0.75,
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, angle = 90),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 12),
        legend.text = element_text(size = 10),
        legend.key.size = unit(1, 'cm'),
        legend.key.height = unit(1, 'cm'))
```

@@

<!--To generate errors for different total number of bins-->
```{r}
#| label: bins-scurve
#| eval: false
## To initialize benchmark values to remove low density hexagons
benchmark_rm_hex_vec <- append(seq(0, 0.99, by=0.1), c(benchmark1, 0.99))

@@

```{r}
#| label: diff-bins-scurve
## To initialize benchmark values to remove low density hexagons
benchmark_rm_hex_vec <- seq(0, 0.8, by=0.1)
bin1_vec_scurve <- c(7, 11, 17)
error_rm_scurve <- data.frame(matrix(nrow = 0, ncol = 0))

    ## Compute error
    error_df <- glance(
      df_bin_centroids = df_bin_centroids_scurve_high_dens,
      df_bin = df_bin_scurve_high_dens,
      training_data = training_data_scurve,
      newdata = NULL,
      type_NLDR = "UMAP",
      col_start = "x") |>
      mutate(benchmark_rm_lwd = benchmark_rm_lwd,
             bin1 = xbins,
             b_non_empty = NROW(df_bin_centroids_scurve_high_dens))

mse_scurve_lwd <- ggplot(error_rm_scurve, 
                     aes(x = benchmark_rm_lwd, 
                         y = MSE,
                         colour = as.factor(bin1),
                         group = as.factor(bin1))) + 
  geom_point(
    size = 1
    ) +
  geom_line(
    linewidth = 0.3
    ) + 
  scale_color_brewer(type = "qual") +
  # geom_vline(xintercept = benchmark1, linetype="solid", 
  #            color = "#bdbdbd", linewidth=1, alpha = 0.5) +
  scale_x_continuous("bechmark to remove low-density hexagons", 
         transform = "reverse") + 
  ylab("MSE") +
  ggtitle("(c)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, 
            angle=90),
        plot.title = element_text(size = 12))
```

### 2024-08-19 paper.tex
Updated Figure 10

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-35-1.pdf}
\end{center}

@@

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-64-1.pdf}
\end{center}

>>>>

\begin{center}
\includegraphics[width=1\textwidth,height=0.3\textheight]{paper_files/figure-pdf/unnamed-chunk-35-1.pdf}
\end{center}

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-36-1.pdf}
\end{center}

@@

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-66-1.pdf}
\end{center}
